The evolution of the transcriptome of mammalian placentas

### 2016-09-08 manuscript/manuscript.Rnw
make xlim smaller for tree plots

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="CGA" &
                                                    species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=2,color="black",fontface="italic")+xlim(0,0.8)+
      theme(legend.position="none"),
      vp=viewport(layout.pos.col=1,layout.pos.row=1,clip="off"))
print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="CGB1" &
                                                    species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                subtree=c("ENSMODG00000013768","ENSG00000104818"),
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=2,color="black",fontface="italic")+xlim(0,1),
      vp=viewport(layout.pos.col=2,layout.pos.row=1,clip="off"))
popViewport(1)
grid.text(c("A","B"),
          x=unit(c(0,2/5),"npc"),y=unit(c(1,1),"npc"),
          just=c("left","top"),
          gp=gpar(fontsize="24")
          )
@ 
\caption{\genetreeexplanation{(A) \textit{CGA} (B) \textit{CGB}}}
\label{fig:cga_cgb_evolution_tree}
\end{figure}

>>>>

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="CGA" &
                                                    species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=2,color="black",fontface="italic")+xlim(0,0.4)+
      theme(legend.position="none"),
      vp=viewport(layout.pos.col=1,layout.pos.row=1,clip="off"))
print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="CGB1" &
                                                    species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                subtree=c("ENSMODG00000013768","ENSG00000104818"),
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=2,color="black",fontface="italic")+xlim(0,0.5),
      vp=viewport(layout.pos.col=2,layout.pos.row=1,clip="off"))
popViewport(1)
grid.text(c("A","B"),
          x=unit(c(0,2/5),"npc"),y=unit(c(1,1),"npc"),
          just=c("left","top"),
          gp=gpar(fontsize="24")
          )
@ 
\caption{\genetreeexplanation{(A) \textit{CGA} (B) \textit{CGB}}}
\label{fig:cga_cgb_evolution_tree}
\end{figure}
